Scikit-learn: machine learning without learning the machinery

### 2014-06-22 article.tex
iter

Goal: enable anybody to contribute, have a controlled process, grow.

>>>>

The greatest asset of the scikit-learn project is its breadth of
contributors, coming from different backgrounds, working in different
institutions, with a variety of applications --xxx contributors total,
xxx active core contributors in the past year--. Indeed, not only is
there strength in numbers, but also the convergence of points of views
make better code and better design. From a developer's perspective, the
project thus is managed with the goals of enabling newcomers to
contribute with a tightly controlled process.
